---
title: "Class09"
author: "Jasmin Revanna"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## K-means clustering

Let's try the 'k-means()' function in R to cluster some made-up example data.

```{r}
tmp <- c(rnorm(30,-3), rnorm(30,3))
x <- cbind(x=tmp, y=rev(tmp))
plot(x)
```

```{r}
km <- kmeans(x, centers=2, nstart=20)
km
```
What is the output object of 'km'
```{r}
attributes(km)
```

```{r}
km$size
```

```{r}
km$cluster
```

Let's check how many 2s and 1s are in this vector

```{r}
table(km$cluster)
```

PLot x colored by the kmeans cluster assignment and ass cluster centers as blue points

```{r}
plot(x, col=km$cluster)
points(km$centers, col="blue", pch=15, cex=3)
```

The 'hclust()' function is the main Hierarchical clustering method in R and it must be passed a distance matrix as input, not your raw data

```{r}
hc <- hclust(dist(x))
hc
```

```{r}
plot(hc)
abline(h=6, col="red", lty=2) 
abline(h=3.5, col="blue", lty=2) 
```
```{r}
cutree(hc, h=6)
```


```{r}
table(cutree(hc, h=3.5))
```


You can also ask 'cutree()' for the 'k' number of groups that you want
```{r}
cutree(hc, k=5)
```



```{r}
# Step 1. Generate some example data for clustering
x <- rbind(
 matrix(rnorm(100, mean=0, sd=0.3), ncol = 2), # c1
 matrix(rnorm(100, mean=1, sd=0.3), ncol = 2), # c2
 matrix(c(rnorm(50, mean=1, sd=0.3), # c3
 rnorm(50, mean=0, sd=0.3)), ncol = 2))
colnames(x) <- c("x", "y")
# Step 2. Plot the data without clustering
plot(x)
# Step 3. Generate colors for known clusters
# (just so we can compare to hclust results)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)
```

Q. Use the dist(), hclust(), plot() and cutree()
 functions to return 2 and 3 clusters
 
```{r}
hclu <- hclust(dist(x))
hclu
```
```{r}
plot(hclu)
```

You can also ask 'cutree()' for the 'k' number of groups that you want
```{r}
grp2 <- cutree(hc, k=2)
```
```{r}
grp3 <- cutree(hc, k=3)
```
```{r}
table(grp3)
```

Q. How does this compare to your known 'col' groups?

```{r}
plot(x, col=grp3)
```

```{r}
table(grp3, col)
```




#Principal Component Analysis (PCA)

The main function in base R for PCA is called 'prcomp()'. Here we will use PCA to examine the funny foods that folks eat in the UK and N. Ireland.

```{r}
x <- read.csv("UK_foods.csv", row.names = 1)
x
```

Make some plots
```{r}
barplot(as.matrix(x), beside = T, col = rainbow(nrow(x)))
```

```{r}
pairs(x, col=rainbow(10), pch=16)
```


#PCA to the rescue!

```{r}
pca <- prcomp(t(x))
```

```{r}
summary(pca)
```

```{r}
attributes(pca)
```

```{r}
plot(pca$x[,1], pca$x[,2], xlab = "PC1 (67.4%)", ylab = "PC2")
text(pca$x[,1], pca$x[,2], colnames(x), col=c("black", "red", "blue", "darkgreen"))
```

