---
title: "Corona Virus"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Coronavirus
Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

A CSV file is available here https://github.com/RamiKrispin/coronavirus-csv


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```

Q1. How many total infected cases are there around the world?

```{r}
total <- sum(virus$cases)
total
```

Q2. How many deaths linked to infected cases have there been?

```{r}
inds <- virus$type=="death"
deaths <- sum(virus[inds,"cases"])
```

Q3. What is the overall death rate?
```{r}
round(deaths/total * 100, 2)
```

Q4. What is the death rate in China?
```{r}
ChinaCases <- (virus$Country.Region == "Mainland China")
totalChinaCases <- sum(virus[ChinaCases, "cases"])

ChinaDeaths <- virus$Country.Region=="Mainland China" & virus$type=="death"
totalChinaDeaths <- sum(virus[ChinaDeaths,"cases"])

round(totalChinaDeaths/totalChinaCases *100, 2)
```


Q5. What is the death rate in Italy, Iran and the US?
```{r}
#Italy
ItalyCases <- (virus$Country.Region == "Italy")
totalItalyCases <- sum(virus[ItalyCases, "cases"])

ItalyDeaths <- virus$Country.Region=="Italy" & virus$type=="death"
totalItalyDeaths <- sum(virus[ItalyDeaths,"cases"])

round(totalItalyDeaths/totalItalyCases *100, 2)

#Iran
IranCases <- (virus$Country.Region == "Iran")
totalIranCases <- sum(virus[IranCases, "cases"])

IranDeaths <- virus$Country.Region=="Iran" & virus$type=="death"
totalIranDeaths <- sum(virus[IranDeaths,"cases"])

round(totalIranDeaths/totalIranCases *100, 2)

#US
USCases <- (virus$Country.Region == "US")
totalUSCases <- sum(virus[USCases, "cases"])

USDeaths <- virus$Country.Region=="US" & virus$type=="death"
totalUSDeaths <- sum(virus[USDeaths,"cases"])

round(totalUSDeaths/totalUSCases *100, 2)
```
