---
title: 'Class 6: R functions'
author: "Jasmin Revanna"
date: "1/24/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is level 2 heading

This is **regular** old *text*!

and a list of stuff


- toy
- garage
- shoe


```{r}
plot(1:5, col="light blue", type="o")
```

let's insert a code chunk with the shortcut `Option-CMD-i`:

```{r}
x <- c(1:10)
x
```

Here is my analysis of your new data. It looks ok.. the mean of your data is `r mean(x)`.

We will use the read.table function
```{r}
x <- read.csv("test1.txt")
```

```{r}
y <- read.table("test2.txt", header = TRUE, sep = "$")
```

```{r}
z <- read.table("test3.txt")
```










## Our first function

This is an example function `add` withinputs a`x` and `y`

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```

Let's try to use it

```{r}
add(x=c(1, 4, 7), y=4)
```


```{r}
rescale2 <- function(x) {
 rng <-range(x, na.rm = TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```


```{r}
rescale2(c(1:10, NA))
```


    
```{r}
rescale <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=TRUE)
 } else {
 rng <-range(x)
 }
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 return(answer)
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
}

```

```{r}
##rescale3(x)
```

## Working with the bio3d package

To use the function from any package we have installed, we use the `library()` function to load it.

```{r}
library(bio3d)
```

# Can you improve this analysis code?
```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```



```{r}
hc <- hclust( dist( rbind(s1.b, s2.b, s3.b) ) )
plot(hc)
```


```{r}
s1 <- read.pdb("4AKE") 
s1
```



```{r}
class(s1)
```

```{r}
str(s1)
```

```{r}
s1$seqres
```


```{r}  
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor") #putting all graphs into 1
points(s2.b, col = "blue", typ = "l")
points(s3.b, col = "red", typ = "l")
```